\hline
Category                             & Example merchant types                         \\ 
\hline
grocery and food                     & 1. grocery stores and super markets; 2. convenience stores; 3. drug stores and pharmacies; 4. miscellaneous retail stores; 5. meat provisioners; 6. bakery, etc. \\
\hline
transportation                       & 1. bus lines; 2. railway stations 3. car rentals;  4. toll and bridge fees, etc.                                                                             \\
\hline

home leisure                         & 1. TV cable fees; 2. digital goods, i.e. games, etc.                                                                                                              \\\hline

housing and utilities                & 1. housing rent payment; 2. home utilities, etc.                                                                                                                  \\\hline

shopping                             & 1. department stores; 2. discount stores; 3. variety stores; 4. general merchandize; 5. wholesale clubs, etc.                                                     \\\hline

eating, drinking and leisure outside home & 1. restaurants; 2. bars/taverns/clubs; 3. different kinds of parks;  4. outdoor sport and sport events; 5. ochestra and theaters, etc.                            \\\hline

IT service                           & 1. computer network; 2. telegraph; 3. telecommunication, etc.                                                                                                     \\\hline

contact-based service                & 1. barber and beauty shops; 2. child care; 3. home cleaning; 4. repair stores; 5. veterinary services; 6. home furnishing; 7. laundry; 8. auto repair, etc.       \\\hline

durables                             & 1.vehicles/motorcycle /auto parts; 2. furniture; 3. home appliance; 4. electronics and equipments; 5. home supplies; 6. music instruments, etc.                   \\\hline

non-contact-based service            & 1. accouting/auditing; 2. business services; 3. programming; 4. consultations; 5. horticultural/ landscaping, etc.                                                \\\hline

clothing, footwear and cosmetics     & 1. clothing stores of different kinds; 2. cosmetic stores; 3. footwear and shoe stores, etc.                                                                      \\\hline

alcohol and tabacco                  & 1. package stores selling wine, beer and other liquor; 2. Cigar and tabacco stores, etc.                                                                          \\\hline

travel                               & 1. airlines; 2. lodging and hotels; 3. duty free stores; 4. airports; 5. travel agencies, etc.                                                                    \\\hline

financial service                    & 1. insurance; 2. money orders; 3. wire transfers, etc.                                                                                                            \\\hline

non-essential stores                 & 1.antique stores; 2. book stores; 3. art dealers, etc.                                                                                                            \\\hline

other                                & 1. public organizations; 2. government fees; 3. educations; 4. medical spending such as dental clinic, etc.                                                       \\ 
\hline
\bottomrule